

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
# Question 1.

```{r}
getPrices <- function(tickers, 
                      as.of.dates=seq(from=as.Date("1962-01-02"), 
                                      to=Sys.Date(), 
                                      by="day"),
                      src="yahoo",
                      api.key=NULL){
  # Get closing prices for a vector of tickers
  # Catch the special ticker "CASHX" and handle carefully
  # Args:
  #   tickers: character vector of ticker symbols
  #   as.of.dates: date, or a vector of dates
  #   src: "yahoo", "av", or "tiingo"
  #   api.key: character string required if src="av" or src="tiingo"
  # Returns:
  #   xts object of closing prices at the given dates
  # Depends on:
  #   getSymbols and Cl functions from package 'quantmod'
  #   if src="av" or src="tiingo", then package 'jsonlite' is also required
  
  print("Getting prices...")
  
  myPrices <- NULL
  for (tkr in tickers) {
    print(tkr)
    if (tkr != "CASHX") {
      # HACK! getSymbols appears to have a bug when src="yahoo" is used.
      # The argument "to" evidently must be one day later than the last desired day!
      tmp <- getSymbols(
        tkr, 
        from=as.of.dates[1], 
        to=(as.Date(tail(as.of.dates, 1)) + 1), 
        src=src,
        api.key=api.key,
        return.class="xts",
        auto.assign=FALSE)
      tmp <- tmp[as.of.dates, ]  # Extract desired dates
      tmp <- Cl(tmp)  # Extract closing prices only
      index(tmp) <- as.Date(index(tmp)) # To fix a weirdness when using src="tiingo"
    }
    else {  # Add a column for CASHX
      tmp <- as.xts(rep(1.0, length(as.of.dates)), as.Date(as.of.dates))
    }
    myPrices <- cbind(myPrices, tmp)
  }#end for
  
  colnames(myPrices) <- tickers
  return(myPrices)
}#end getPrices

library(quantmod)
myTickers <- c("AAPL", "AMZN", "BABA", "COST", "DIS", "DPZ", "F", "FB", "GOOGL",
               "H", "KR", "KO", "MMM", "MSFT", "PG", "SBUX", "T","UNP","UPS", 
               "TSLA", "CASHX")


as.of.dates <- c("2022-03-25")
myPrices <- getPrices(myTickers, as.of.dates)
print(myPrices)
```

Use the writeHoldings function to write a holdings text file

```{r}
writeHoldings <- function(account.name, as.of.date, tickers, num.shares){
  # Write holdings to a csv file named like "H-uwid-2022-03-25.csv"
  # Args:
  #   account.name: account identifier
  #   as.of.date: date of the holdings, ccyy-mm-dd format
  #   tickers: character vector of ticker symbols
  #   num.shares: numeric vector of numbers of shares
  # Returns:
  #   data frame containing the columns written to the file
  
  # Make a data frame
  holdings <- data.frame(
    ticker = tickers,
    num.shares = num.shares,
    stringsAsFactors = FALSE)
  
  # Compose the file name
  filename <- paste("H-", account.name, "-", as.Date(as.of.date), ".csv", sep="")
  
  # Write to a file
  write.csv(holdings, file=filename, row.names=FALSE)

  return(holdings)
}#end writeHoldings

# Example of use
uwid <- "ning2021"

aDate <- "2022-03-25"

myTickers <- c("AAPL", "AMZN", "BABA", "COST", "DIS", "DPZ", "F", "FB", "GOOGL",
               "H", "KR", "KO", "MMM", "MSFT", "PG", "SBUX", "T","UNP","UPS", 
               "TSLA", "CASHX")

#set my own shares
myShares <- c(230, 50, 100 ,110, 100, 100, 300, 150, 70, 120, 300, 200, 300, 
              200, 320, 200, 220, 110, 250, 100, 30637.77)

(initial.value <- myPrices %*% myShares) #check the initial value 1M

#calculate the weights
calcWeights <- function(values) {
  # Calculate weights from a vector of values
  # Args:
  #  values: vector of values
  # Returns:
  #  vector of weights that sum to 100
  
  portvalue <- sum(values)
  weights <- (values / portvalue) * 100
  return(weights)
}# end calcWeights

weights <- calcWeights(myPrices * myShares)
print(weights)
sum(weights[,1:21])

#Transaction fee (buying the equities)
tc1 <- 0.001 * (initial.value - myShares[21] *1)
print(tc1)

#update the Liquidity reserve
myShares.2 <- myShares
myShares.2[21] <- myShares[21] - tc1

tmp <- writeHoldings(uwid, aDate, myTickers, myShares.2)
# To save the data frame in your workspace, give it unique name
dfName <- paste("H", uwid, make.names(aDate), sep=".")
assign(dfName, tmp)

#check the total value
(total.value1 <- myPrices %*% myShares.2)

weights.2 <- calcWeights(myPrices * myShares.2)
print(weights.2)
sum(weights.2[,1:21])

```

Checking the guidelines are satisfied.

```{r}
#value of portfolio V0
deposit <- 1000000
V0 = deposit - tc1
print(V0)
```

# Question 2.

```{r}
#Return on 3-25-2022
(r1 <- (V0 - deposit)/deposit)
```

# Question 3.
```{r}
getSplitfactors <- function(tkr, 
                            as.of.dates=seq(from=as.Date("1962-01-02"), 
                                            to=Sys.Date(), 
                                            by="day"),
                            src="yahoo",
                            api.key=NULL){
  # Get cumulative split factors between dates
  # Args:
  #   tkr: a character ticker symbol
  #   as.of.dates: a vector of two or more dates
  #   src: only "yahoo" is valid at present
  #   api.key: character string required if src="av" or src="tiingo" (not valid at present)
  # Returns:
  #   xts object of cumulative split factors between the given dates
  # Depends on:
  #   getSplits function from package 'quantmod'
  
  print(paste("Getting split factors for ticker", tkr, sep=" ")) 
  
  splitfactors <- 1
  for (t in 2:length(as.of.dates)){
    # HACK! getSplits appears to have a bug when src="yahoo" is used.
    # The argument 'to' evidently must be one day later than the last desired day!
    splits <- getSplits(tkr, 
                        from=(as.Date(as.of.dates[t - 1]) + 1), 
                        to=as.Date(as.of.dates[t]) + 1,
                        src=src,
                        api.key=api.key,
                        return.class="xts",
                        auto.assign=FALSE)
    splits.cum <- prod(splits)
    if (is.na(splits.cum)){
      splits.cum <- 1
    }
    splitfactors <- c(splitfactors, splits.cum)
  }#end for
  
  splitfactors.xts <- as.xts(splitfactors, as.Date(as.of.dates))
  colnames(splitfactors.xts) <- tkr
  return(splitfactors.xts)
}#end getSplitfactors

library(quantmod)
as.of.dates = c("2022-03-25","2022-04-01")
myTickers <- c("AAPL", "AMZN", "BABA", "COST", "DIS", "DPZ", "F", "FB", "GOOGL",
               "H", "KR", "KO", "MMM", "MSFT", "PG", "SBUX", "T","UNP","UPS", 
               "TSLA", "CASHX")

# Calling getSplits returns the individual dates and split factors
for (tkr in myTickers) {
  print(getSplits(tkr))
}

# With getSplitfactors, the dates are aligned
splitfactors <- NULL
for (tkr in myTickers){
  if (tkr != "CASHX"){
    # Get split factors
    tkrtmp <- getSplitfactors(tkr, as.of.dates)
    splitfactors <- cbind(splitfactors, tkrtmp)
  }
}
# Add a column for CASHX
colnames(tkrtmp) <- "CASHX"
tkrtmp[ , "CASHX"] <- 1.0
splitfactors <- cbind(splitfactors, tkrtmp)
print(splitfactors)

# Adjust holdings
myHoldings <- data.frame(ticker=myTickers, initial.shares= myShares.2)
for (idate in 1:length(as.of.dates)){
  adjustedHoldings <- myHoldings[ , idate + 1] / as.numeric(splitfactors[idate, ])
  myHoldings <- cbind(myHoldings, adjustedHoldings)
}
colnames(myHoldings) <- c("ticker", "initial.shares", as.of.dates)
print(myHoldings)
```
No splits occurred between 25 March and 1 April of my stocks.

# Question 4.

```{r}
getDivpershare <- function(tkr,
                           as.of.dates=seq(from=as.Date("1962-01-02"),
                                           to=Sys.Date(), 
                                           by="day"), src="yahoo",
                           api.key=NULL){
  # Get cumulative dividend per share between dates
  # Args:
  #   tkr: a character ticker symbol
  #   as.of.dates: a vector of two or more dates
  #   src: only "yahoo" is valid at present
  #   api.key: character string required if src="av" or src="tiingo" (not valid at present)
  # Returns:
  #   xts object of cumulative dividend per share between the given dates
  # Depends on:
  #   getDividends function from package 'quantmod'
  
  print(paste("Getting dividends per share for ticker", tkr, sep=" "))
  
  divps <- 0
  for (t in 2:length(as.of.dates)){
    # HACK! getDividends appears to have a bug when src="yahoo" is used.
    # The argument 'to' evidently must be one day later than the last desired day!
    # ALSO: Sometimes a result is returned for a date one day before the 'from' day!
    # To be safe, the 'from' day is advanced by two. 
    # If as.of.dates[t - 1] is a Friday, then as.Date(as.of.dates[t - 1]) + 2 is a Sunday.
    div <- getDividends(tkr, 
                        from=(as.Date(as.of.dates[t - 1]) + 2), 
                        to=(as.Date(as.of.dates[t]) + 1),
                        src=src,
                        api.key=api.key,
                        return.class="xts",
                        auto.assign=FALSE)
    div.cum <- sum(div)
    if (is.na(div.cum)){
      div.cum <- 0
    }
    divps <- c(divps, div.cum)
  }#end for
  
  divps.xts <- as.xts(divps, as.Date(as.of.dates))
  colnames(divps.xts) <- tkr
  return(divps.xts)
}#end getDivpershare

library(quantmod)
as.of.dates = c("2022-03-25","2022-04-01")
myTickers <- c("AAPL", "AMZN", "BABA", "COST", "DIS", "DPZ", "F", "FB", "GOOGL",
               
               "H", "KR", "KO", "MMM", "MSFT", "PG", "SBUX", "T", "UNP", "UPS",
               "TSLA", "CASHX")

# Calling getDividends returns the individual dates and dividend per share
for (tkr in myTickers) {
  print(getDividends(tkr))
}

# With getDivpershare, the dates are aligned
divps <- NULL
for (tkr in myTickers){
  if (tkr != "CASHX"){
    # Get dividend per share
    tkrtmp <- getDivpershare(tkr, as.of.dates)
    divps <- cbind(divps, tkrtmp)
  }
}
# Add a column for CASHX
colnames(tkrtmp) <- "CASHX"
tkrtmp[ , "CASHX"] <- 0.0
divps <- cbind(divps, tkrtmp)
print(divps)

# Calculate dividend amounts
# Holding 100 shares of each security
myDividendValues <- data.frame(ticker=myTickers, num.shares= myShares.2)
for (idate in 1:length(as.of.dates)){
  dividendValue <- myDividendValues[ , 2] * as.numeric(divps[idate])
  myDividendValues <- cbind(myDividendValues, dividendValue)
}
colnames(myDividendValues) <- c("ticker", "num.shares", as.of.dates)
print(myDividendValues)
```
No dividends distributed between 25 March and 1 April.

# Question 5. 
```{r}
myTickers <- c("AAPL", "AMZN", "BABA", "COST", "DIS", "DPZ", "F", "FB", "GOOGL",
               "H", "KR", "KO", "MMM", "MSFT", "PG", "SBUX", "T","UNP","UPS", 
               "TSLA", "CASHX")

as.of.dates <- c("2022-04-01")
myPrices.2 <- getPrices(myTickers, as.of.dates)
print(myPrices.2)
```

```{r}
#the account value
#av <- myPrices.2 %*% myShares.2
#print(av)

#management fee per week
fee <- V0 * 0.0002
print(fee)

#update liquidity reserve on 1 April 2022
myShares.3 <- myShares.2
(myShares.3[21] <- myShares.2[21] - fee)

```


The weekly management fee = $199.8061
The liquidity reserve on 1 April 2022 is: 28,383.65 - 201.12 =  $29,468.6.

# Question 6.
```{r}
tc2 <- 0.2 * 50 * as.numeric(myPrices.2[,2]) * 0.001
tc3 <- 500 * as.numeric(myPrices.2[,12]) * 0.001
tc4 <- 0.2 * 100 * as.numeric(myPrices.2[,20]) * 0.001
tc5 <- 130 * as.numeric(myPrices.2[,15]) * 0.001

#total transaction fee
tc.sum <- sum(tc2,tc3,tc4,tc5)
print(tc.sum)

#trading earnings
te <- 10 * as.numeric(myPrices.2[,2]) - 500 * as.numeric(myPrices.2[,12]) + 20 * as.numeric(myPrices.2[,20])- 130 * as.numeric(myPrices.2[,15])
print(te)

#update the shares
myShares.4 <- myShares.3
myShares.4[2] <- myShares.3[2] - 0.2 * myShares.3[2]
myShares.4[12] <- myShares.3[12] + 500
myShares.4[20] <- myShares.3[20] - 0.2 * myShares.3[20]
myShares.4[15] <- myShares.3[15] + 130
myShares.4[21] <- myShares.3[21] - tc.sum + te
```


```{r}
#the value of the portfolio V1 on 2022-04-01

V1 <- myPrices.2 %*% myShares.4  #(total value - transaction cost - management fee) + trading earnings
print(V1)

#The liquidity reserve on 1 April 2022 
myShares.4[21]

weights.3 <- calcWeights(myPrices.2 * myShares.4)
print(weights.3)
sum(weights.3[,1:21])
```
Selling 20% shares of "AMZN", at the same time buying 500 shares of "KO";

Selling 20% shares of "TSLA", and buying 130 shares of "PG".

The liquidity reserve on 1 April 2022 is: $3,2031.84.

The total value of the portfolio: $1,004,303.

Checking the guidelines are satisfied.

```{r}
#Use the writeHoldings function to write a holdings text file for 2022-04-01.
uwid <- "ning2021"
aDate <- "2022-04-01"

myTickers <- c("AAPL", "AMZN", "BABA", "COST", "DIS", "DPZ", "F", "FB", "GOOGL",
               "H", "KR", "KO", "MMM", "MSFT", "PG", "SBUX", "T","UNP","UPS", 
               "TSLA", "CASHX")
tmp <- writeHoldings(uwid, aDate, myTickers, myShares.4)

# To save the data frame in your workspace, give it unique name
dfName <- paste("H", uwid, make.names(aDate), sep=".")
assign(dfName, tmp)
```

# Question 7.
```{r}
#income return = 0
ir <- 0
#price return
pr <- (V1 - V0)/V0
#total return
tr <- ir + pr

print(ir)
print(pr)
print(tr)
```
At the week ending 2022-04-01:
Income return: 0
Price return: 0.005277351
Total rate of return: 0.005277351

# Question 8.
```{r}
writeAccountSummary <- function(account.name, as.of.dates, deposits, withdrawals, 
                                dividends, fees, tc, values, 
                                income.returns, price.returns, total.returns) {
  # Write an account summary file in .csv format named like "A-uwid-2022-04-01.csv"
  # Args:
  #   account.name: account identifier
  #   as.of.dates: vector of dates, ccyy-mm-dd format
  #   deposits: numeric vector of deposit amounts
  #   withdrawals: numeric vector of withdrawal amounts
  #   dividends: numeric vector of dividend amounts
  #   fees: numeric vector of fee amounts
  #   tc: numeric vector of transaction cost amounts
  #   values: numeric vector of account values
  #   income.returns: numeric vector of period income returns between dates
  #   price.returns: numeric vector of period price returns between dates
  #   total.returns: numeric vector of period total returns between dates
  # Returns:
  #   data frame containing the columns written to the file

  numDates <- length(as.of.dates)
  
  # Make a data frame
  AccountSummary <- data.frame(
    account.name = rep(account.name, numDates),
    as.of.date = as.of.dates,
    deposits = deposits,
    withdrawals = withdrawals,
    dividends = dividends,
    fees = fees,
    tc = tc,
    value = values,
    income.return = income.returns,
    price.return = price.returns,
    total.return = total.returns,
    stringsAsFactors = FALSE)

  # Compose the file name
  filename <- paste("A-", account.name, "-", tail(as.of.dates, 1), ".csv", sep="")
  
  # Write to a file
  write.csv(AccountSummary, file=filename, row.names=FALSE)

  return(AccountSummary)
}#end writeAccountSummary

# Example of use
uwid <- "ning2021"
dates <- c("2022-03-25", "2022-04-01")
deposits <- c(1000000, 0)
withdrawals <- c(0, 0)
dividends <- c(0, 0)
fees <- c(0, fee)
tc <- c(tc1, tc.sum)
values <- c(V0, V1)
incomereturns <- c(0, 0)
pricereturns <- c(r1, pr)
totalreturns <- c(r1, tr)

AccountSummary <- writeAccountSummary(uwid, dates, deposits, withdrawals, dividends, fees, tc, values,
                           incomereturns, pricereturns, totalreturns)

# To save the data frame in your workspace, give it unique name
dfName <- paste("A", uwid, make.names(tail(dates, 1)), sep=".")
assign(dfName, AccountSummary)

```


